---
title: "Education"
---
```{r fig.width=3, fig.height=3,echo=FALSE}

library(vembedr)
library(png)
library(grid)

img <- readPNG(here::here("gvsu.png"))
grid.raster(img)

```

## Grand Valley State University

BS in Statistics (anticipated 2023)  
* minor in Economics  

MS in Applied Statistics (anticipated 2024)

### Student Initiated Combined Degree
I am currently enrolled in a student initiated combined degree program (SICD) which enables me to take both graduate and undergraduate courses which will allow me to achieve my MS one year earlier than would be normal.

### Notable Achievements

Dean's List 2020 - 2021 - 2022: This requires maintaining a GPA of at least 3.5 throughout the school year.  
  
Maintaining a GPA above 3.8 throughout University (current GPA 3.87).

### Extracuricular Activities

Statistics Club: A club that organizes many events including career and advising events, math/statistics software workshops, and social gatherings.

Model UN: A club that prepared us for the Model UN. This was a yearly event where different schools sent "delegates" from different countries to meet and simulate a UN meeting to resolve a designated issue.
  
  
```{r fig.width=3, fig.height=3,echo=FALSE}

img <- readPNG(here::here("fhs.png"))
grid.raster(img)

```


## Fowlerville High School

High School Diploma (2019) - 4.03 GPA

### Notable Achievements

Academic Letter (2015-2019) - Awarded for maintaining a high GPA of 3.5 throughout High School.

VFW Scholarship (2019) - Awarded 1st place in an essay competition with the topic "Why is it important to vote?".

Outstanding Achievement in Biology and US History (2019) - Awarded to one student in that year for outstanding achievement in a specific class.

### Extracuricular Activites

Robotics Club - This club worked to design a robot to accomplish a certain task involved collecting data on other robots to build your alliances later on in the competition.

National Honor Society (NHS) - This group did community work and projects while maintaining good academic performance.

Jazz Band - This club met twice a week to practice jazz music that we would perform at certain music festivals later in the year.

Brass Quintet - This was a weekly club that met and practiced quintet music for performances. We also caroled on Christmas.