---
title: "Education"
---
```{r fig.width=3, fig.height=3,echo=FALSE}

library(vembedr)
library(png)
library(grid)

img <- readPNG(here::here("gvsu.png"))
grid.raster(img)

```

## Grand Valley State University

BS in Statistics (anticipated 2023)  
* minor in Economics  

MS in Applied Statistics (anticipated 2024)

### Student Initiated Combined Degree
I am currently enrolled in a student initiated combined degree program (SICD). This mean I am currently taking both graduate and undergraduate courses which will allow me to achieve my MS one year earlier than would be normal.

### Notable Achievements

Deans List 2020 - 2021 - 2022: This requires maintaining a GPA of at least 3.5 throughout the school year   
  
Maintaining a GPA above 3.8 throughout University  

### Extracuricular Activities

Statistics Club: A club meeting monthly that discussed statistics and gave opportunites to meet with potential employers and former alumni. 

Model UN: Club meeting weekly that prepared for the Model UN a yearly event where different schools sent "delegates" from different countries to meet and simulate a UN meeting to resolve a designated issue
  
  
```{r fig.width=3, fig.height=3,echo=FALSE}

img <- readPNG(here::here("fhs.png"))
grid.raster(img)

```


## Fowlerville High School

High School Diploma (2019)

### Notable Achievements

Academic Letter (2015-2019) - awarded for maintaining a high GPA of 3.5 throughout High School  

VFW Scholarship - awarded in an essay competition where the best essay about why it was important to vote

Outstanding Achievement in Biology and US History - awarded to one student in that year for oustanding achievement in a specific class

### Extracuricular Activites

Robotics Club - worked to design a robot to accomplish a certain task involved collecting data on other robots to build your alliances later on in the competition 

National Honor Society (NHS) - worked to do community work and projects while maintaining good academic performance

Jazz Band - a bi-weekly club that met and practiced jazz music to eventually perform at certain music festivals later in the year

Brass Quintet - a weekly club that met and practiced quintet music for performances also caroling on Christmas 